### 2016-07-06 Docs/FAQ/faq.tex

\boxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  Compile with {\tt
  TEST=t} \otherindex{{\tt GNUmakefile}}{TEST=t} in your {\tt GNUmakefile} (this is also
activated in debug-mode, with {\tt NDEBUG= }).  The floating point
exceptions include NaNs, divide by zero, and overflow.  When one of
these is hit, the code will abort, and the backtrace information will
be output to a file {\tt Backtrace.N}, where {\tt N} is the processor
number.  BoxLib will also initialize \multifab s with signaliing NaNs
to help uncover any floating point issues.

Handling of seg faults and interruption by control-C are always
enabled, so you can get a backtrace from the code by interrupting its
execution on the commandline (this can be useful for investigating
deadlocks).

Behind the scenes, \boxlib\ implements this capability via the
Linux/Unix {\tt feenableexcept} function (this is in {\tt
  backtrace\_c.cpp} in \boxlib).

Note that due to issues with header files, this backtrace capability
is not supported with the PGI compilers.

>>>>

\boxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  See \S
\ref{ch:makefiles:special}.

### 2016-07-06 Docs/getting_started/getting_started.tex

>>>>

\section{Development Model}

When you close \maestro\ from github, you will be on the {\tt master}
branch of the repo.  New changes to \maestro\ are first introduced
into the {\tt development} branch in the \maestro\ git repository.
Nightly regression tests are run on {\tt development} to ensure that
our answers don't change.  Around the first work day of each month, we
merge from {\tt development} $\rightarrow$ {\tt master} (assuming
tests pass) and tag the state of the code with a date-based tag {\tt
  YY-MM}.  We do this on all the other repos in the \boxlib-ecosystem,
including {\tt BoxLib/}, {\tt Microphysics/}, and {\tt Castro/}.

If you want to contribute to \maestro's development, issue a pull-request
through github onto the {\tt development} branch.

### 2016-07-06 Docs/makefiles/makefiles.tex
add runtime parameters for boxlib backtracing
now boxlib_fpe_invalid, boxlib_fpe_zero, and boxlib_fpe_overflow
turn on/off FPE handling through the boxlib backtrace module

\section{Special Debugging Executables}

@@

  Setting {\tt TEST := t}\otherindex{{\tt GNUmakefile}}{TEST=t} will
  enable routines in \boxlib\ that intercept floating point
  exceptions, including NaNs, divide by zero, and overflow.  When one
  of these is hit, the code will abort, and the backtrace information
  will be output to a file {\tt Backtrace.N}, where {\tt N} is the
  processor number.  BoxLib will also initialize \multifab s with
  signaliing NaNs to help uncover any floating point issues.

@@

>>>>

\section{Special Debugging Modes}

\label{ch:makefiles:special}

@@

  Setting {\tt TEST := t}\otherindex{{\tt GNUmakefile}}{TEST} will
  enable routines in \boxlib\ initialize multifabs and arrays 
  allowed via {\tt bl\_allocate} to signalliing NaNs.  This behavior
  is the same as {\tt NDEBUG :=}, but {\tt TEST := t} uses the 
  same compiler optimizations as a normal build.

  This can be useful with compiler flags that trap floating point
  exceptions (FPEs), but checks on floating point exceptions can also
  be enabled through runtime parameters passed to \boxlib's
  backtrace functionlity:
  \begin{itemize}
  \item \runparam{boxlib\_fpe\_invalid}: enabling FPE trapping for
    invalid operations (e.g. {\tt 0 * inf}, {\tt sqrt(-1)})

  \item \runparam{boxlib\_fpe\_zero}: enable FPE trapping for
    divide-by-zero

  \item \runparam{boxlib\_fpe\_overflow}: enable FPE trapping for
    overflow
  \end{itemize}

\item backtracing

  When exception trapping is enabled (either via \boxlib\ or the
  compiler), the code will abort, and the backtrace information will
  be output to a file {\tt Backtrace.N}, where {\tt N} is the
  processor number.  BoxLib will also initialize \multifab s with
  signaliing NaNs to help uncover any floating point issues.

@@

  Note: you will need to have the libraries {\tt libasan} and {\tt
    libubsan} installed on your machine to use this functionality.

### 2016-07-06 Docs/runtime_parameters/runtime_parameters.tex

%%%%%%%%%%%%%%%%
% symbol table
%%%%%%%%%%%%%%%%

@@

\rowcolor{tableShade}
\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\
\verb=  limit_conductivity  = &   apply the conductivity limiting---if T, then we set the thermal coefficients all to 0 for $\rho <$ {\tt buoyancy\_cutoff\_factor} * {\tt base\_cutoff\_density}  &  .false. \\
\rowcolor{tableShade}
\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\
\rowcolor{tableShade}
\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\

@@

>>>>

@@

\rowcolor{tableShade}
\verb=  limit_conductivity  = &   apply the conductivity limiting---if T, then we set the thermal coefficients all to 0 for $\rho <$ {\tt buoyancy\_cutoff\_factor} * {\tt base\_cutoff\_density}  &  .false. \\
\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
\rowcolor{tableShade}
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\
\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\

@@

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[gamma law general  EOS parameters.]{gamma law general  EOS parameters.} \label{table: gamma law general  EOS parameters. runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  eos_assume_neutral  = &   do we assume that all the species are neutral atoms? otherwise, we assume complete ionization  &  .true. \\
\verb=  eos_gamma  = &   the constant ratio of specific heats ($\gamma$)  &  5.d0/3.d0 \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[generic network parameters parameters.]{generic network parameters parameters.} \label{table: generic network parameters parameters. runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  small_x  = &   cutoff for species mass fractions  &  0.0 \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[constant conductivity parameters.]{constant conductivity parameters.} \label{table: constant conductivity parameters. runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\
